\cvsection{Experience}
\begin{cventries}
  \cventry
    {9DWLAB}
    {Co-founder \& Chief Operating Officer}
    {Tokyo, Japan}
    {Dec. 2018 - Present}
    {
      \begin{cvitems}
        \item {Architect of IYO, A Smart Peer-to-Peer Distributed Intelligence}
        \item {Design and implement business strategies, plans and procedures.}
        \item {Establish policies that promote company vision and mission.}
        \item {Product design and negociation with the clients.}
      \end{cvitems}
    }
    \cventry
    {9DW}
    {Chief Artificial Intelligence Officer}
    {Tokyo, Japan}
    {April. 2017 - Present}
    {
      \begin{cvitems}
        \item {Apply machine learning and AI methods into client work spanning a range of use cases including exploratory\\
         insights, predictive modeling reporting, and optimization.}
        \item {Develop innovative solutions for client work built into standardized methods.}
        \item {Supervision of 15 engineers (project management, axis of research, code review...).}
      \end{cvitems}
    }
    \cventry
    {9DW}
    {Principal AI engineer}
    {Tokyo, Japan}
    {Feb. 2016 - Present}
    {
      \begin{cvitems}
        \item {Speech recognition system developer, data analyst and model architect.}
        \item {Earthquake prediction based on EMD/IMF and LSTM neural network.}
        \item {Development of patented solution for the generation of dental mesh.}
        \item {Brain anomaly detection based on KL divergence using VAE.}
        \item {Building reconstruction based on genetic algorithms.}
        \item {Setup of server Linux and services AWS/GCP/AZURE.}
      \end{cvitems}
    }
  \cventry
    {WASEDA UNIVERSITY}
    {Research Assistant / Data Analyst}
    {Tokyo, Japan}
    {Oct. 2015 - Mar. 2017}
    {
      \begin{cvitems}
        \item {Matlab developer using NARX (nonlinear autoregressive with exogenous input) for  causality detection.}
        \item {Signal processing and causality quantification from CMS using Matlab Neural Nets toolbox.}
        \item {Improvement of pre-processing methods for causality detection using KNN/FKNN.}
      \end{cvitems}
    }
  \cventry
    {TOKYO UNIVERSITY OF AGRICULTURE AND TECHNOLOGY}
    {Research Assistant / AI Architect}
    {Tokyo, Japan}
    {Oct. 2015 - Feb. 2016}
    {
      \begin{cvitems}
        \item {Software architect of a new hybrid architecture HREP-3 for multi-modal analysis of interaction in HRI.}
        \item {Software development in C\# for head tracking with KinectV2 from Microsoft.}
        \item {Android developer for an application of data visualization under Unity3D in C\#.}
        \item {Unity3D interactive game «Magic Trick» using Pepper from Aldebaran Robotics.}
         \item{Modules developed: NLP (ALICE - Java), Vision (Anaconda -Python), Multi-threading for Client/Server (Python).}
        \end{cvitems}
    }
    \cventry
    {ISIR/CNRS}
    {Reasearch Intern / Data Analyst}
    {Paris, France}
    {Jun. 2014 - Nov. 2014}
    {
      \begin{cvitems}
       \item{Developer C++ of OpenSmile for large-scale feature extractor from multimedia files.}
       \item {SVM technique used for detection of social commitment with voice signal in the first universe age with 75 \% accuracy.}
       \item {Cluster of computers for data analysis.}
      \end{cvitems}
    }
    \cventry
    {LIP6/CNRS}
    {Reasearch Intern / Software Developer}
    {Paris, France}
    {Jan. 2014 - May. 2014}
    {
      \begin{cvitems}
       \item{Developer of WEKA OpenSource library for Data Mining in JAVA. }
       \item {Development and integration of semi-supervised module.}
       \item {Proposal and optimization for cluster detection.}
       \item {Contribution for cluster detection with linear complexity O(n) in time and memory.}
      \end{cvitems}
    }
    \cventry
    {LIRMM/CNRS/EUROMOV}
    {Reasearch Intern / Robot Vision}
    {Montpellier, France}
    {Jun. 2013 - Sept. 2013}
    {
      \begin{cvitems}
       \item{Developer C++ of tracking system with OpenCV on mobile robots.}
       \item {Creation of detailed test plans and test cases.}
       \item {Test and demonstration for EUROMOV (European Center for Research on Human Movement) inauguration.}
      \end{cvitems}
    }
\end{cventries}
